`localHierarchy`: an R package to facilitate fitting of global and local Bayesian hierarchical models

### 2025-09-10 paper/paper.qmd
move intro and application to overleaf

# Introduction

to finish:

-   context: global health estimation exercises, use of bayesian hier models, examples

-   need for local models

    -   We want local Bayesian models to allow users to do runs on their own laptops/get results quickly, use data from own country only, not to get updates when other country is updated.

    -   Examples of where local models are used: maternal, fp. where they could be used ....

-   challenges with global-local combis: no easy set up to keep code in synch between global and local model, to pass parameters from global model on to local model

-   this paper: introduce a package to facilitate development and fitting of combined global-local models. Models fitted in Stan.

>>>>

# Introduction
see overleaf
